*Please Participate in Review of Important <br/> Amberson Towers Condominium Documents*

### 2022-02-09 index.Rmd
Further fix URLs in index.html
Even for link errors - learnin gow Gitpages handles links
moved index file to docs dir
updated title

---
title: "*Please Participate in Review Important <br/> Amberson Towers Condominium Documents*"
author: "A Request from the Governance Committee <br/> of the Amberson Towers Condominium Council"
date: "2/8/2022"
output: html_document
---

@@

* [*As an Adobe PDF document*](DraftRules.html)

* *As a web page*

>>>>

---
title: "*Please Participate in Review of Important <br/> Amberson Towers Condominium Documents*"
author: "A Request from the Governance Committee <br/> of the Amberson Towers Condominium Council"
date: "2/8/2022"
output: html_document
---

@@

* [*As an Adobe PDF document*](DraftRules.pdf)

* [*As a web page*](DraftRules.html)

## *This shell is under development..more to come*
